Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-27 paper/main.tex
show data alongside heterogeneic growth rates for application 2

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.24\textwidth]
        {../data/crm_divide/0003/images/001044.png}%
        \node at (0.02, 0.98)[anchor=north west, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.24\textwidth]
        {../data/crm_divide/0003/images/001054.png}%
        \node at (0.02, 0.98)[anchor=north west, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.24\textwidth]
        {../data/crm_divide/0003/images/001063.png}%
        \node at (0.02, 0.98)[anchor=north west, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.24\textwidth]
        {../data/crm_divide/0003/images/001074.png}%
        \node at (0.02, 0.98)[anchor=north west, white, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \caption{TODO insert segmentation masks here}
    \label{fig:application-2-data-overview}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.49\textwidth]
        {figures/data/crm_fit/001044.png}%
        \node at (0.02, 0.98)[anchor=north west, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.49\textwidth]
        {figures/data/crm_fit/001044-markers.pdf}%
        \node at (0.02, 0.98)[anchor=north west, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.28\textwidth]
        {figures/crm_fit-data-progression.png}
        \node at (0.02, 0.98)[anchor=north west, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.35\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/rod-lengths-individual.pdf}%
        \node at (0, 1)[anchor=north west, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.35\textwidth]
        {figures/crm_estimate_params/IWF-Goettingen/growth-rates-bar-plot.pdf}%
        \node at (0, 1)[anchor=north west, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \caption{
        \textbf{TODO also insert vertical in (B) line to indicate when direct comparison algorithm
        starts.}
        \textbf{Link to supplement for discussion of bar plot}\\
        (A) Snapshot of used microscopic images.
        (B) Segmented microscopic image.
        (C) Selected time points of the utilized time series showcasing the spatial configurations
        of the investigated bacteria.
        A complete list of snapshots is included in the supplementary material (see
        section~\ref{sec:supplement-data-details}).
        (D) Growth curves of individual bacteria including a discrete delay before exponential
        growth is experienced.
        (E) Distribution of growth parameters shows cell-cell variability of the analyzed sample.
        The obtained results are further discussed in the supplementary material section~\ref{}.
    }
    \label{fig:application-2-data-overview}
\end{figure}
